%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

	
	\cventry
	{SWE Intern} % Event
	{Visa - Intern} % Project Name
	{Visa Global HQ, Foster City, CA} % Location
	{May. 2019 - Aug. 2019} % Date(s)
	{ % Description(s) of experience/contributions/knowledge
		\begin{cvitems}
			\setlength{\itemindent}{.125in}
			\item {Developed a management console for task processors using \textbf{Golang}.}
			\item {Implemented authentication system using \textbf{Private/Public} Key Encryption. }
			\item {Interfaced with project leads to accurately plan and map out project spec and scope.}
		\end{cvitems}
	}
	
	%------------------------------------------------
	
	\cventry
	{Freelance Desktop Application} % Event
	{Polysubstance Abuse Survey} % Project Name
	{University of Florida} % Location
	{Jan. 2019 - June. 2019} % Date(s)
	{ % Description(s) of experience/contributions/knowledge
		\begin{cvitems}
			\setlength{\itemindent}{.125in}
			\item {Managed project using the \textbf{Agile} design process in order to provide our client with as much flexibility as possible.}
			\item {Maintained constant contact with the client to update the requirements throughout the project time-line.}
			\item {Utilized \textbf{Electron}, \textbf{React}, and \textbf{Material-UI} to create a fluid, simple to use interface. }
			\item {Designed extensive algorithms to shape the output data into the client's end-user specifications.}
		\end{cvitems}
	}
	%------------------------------------------------	
	
	%------------------------------------------------
	
	\cventry
	{3D OpenGL Game Engine} % Event
	{Madd Engine - Lead Developer} % Project Name
	{University of Florida} % Location
	{Jan. 2018 - Present} % Date(s)
	{ % Description(s) of experience/contributions/knowledge
		\begin{cvitems}
			\setlength{\itemindent}{.125in}
			\item {Implemented scalable object-oriented structure in \textbf{C++} with a Core Game Context and additional on-demand submodules.}
			\item {Lead our dev team in designing important modules, and identifying needed features for later versions of Madd.}
			\item {Utilized \textbf{GLFW} and \textbf{OpenGL}, \textbf{ASSIMP}, and \textbf{BULLET} for Graphics, Asset Management, and collisions.}
			\item {Goal was to create a stable game design framework that is easily understood by beginning game and engine devs.}
		\end{cvitems}
	}
	
	%------------------------------------------------
	
	\cventry
	{Programming Language Concepts} % Event
	{LLVM - OCamlBC} % Project Name
	{University of Florida} % Location
	{Jul. 2018} % Date(s)
	{ % Description(s) of experience/contributions/knowledge
		\begin{cvitems}
			\setlength{\itemindent}{.125in}
			\item {Created language grammar using \textbf{OCamllex} and \textbf{Menhir}.}
			\item {Designed a REPL/Abstract syntax tree parser with \textbf{OCaml}.}
			\item {Implemented \textbf{LLVM} structure in OCaml to create a basic language compiler.}
		\end{cvitems}
	}
	%------------------------------------------------

	
\end{cventries}
