%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Involvement}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

\cventry
{Project Manager} % Affiliation/role
{Association of Computer Engineers} % Organization/group
{University of Florida} % Location
{Dec. 2018 - Dec. 2019} % Date(s)
{ % Description(s) of experience/contributions/knowledge
	\begin{cvitems}
		\setlength{\itemindent}{.125in}
		\item {Planned tech talks with workshop chair to introduce new topics and concepts to members..}
		\item {Developed project ideas and plan of action with project chair to provide members with an opportunities to build on projects.}
	\end{cvitems}
}

%------------------------------------------------

%------------------------------------------------

\cventry
{Project Chair} % Affiliation/role
{Association of Computer Engineers} % Organization/group
{University of Florida} % Location
{Jul. 2017 - Dec. 2018} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\setlength{\itemindent}{.125in}
\item {Led a team of ACE members to develop a fully featured software hardware project.}
\item {Worked with executive board and other chair members to manage the project.}
\item {Participated in a workshop committee to help design and put on workshops for the UF community. }
\item {Volunteered at community outreach programs.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Mentor} % Affiliation/role
{Association of Computer Engineers} % Organization/group
{University of Florida} % Location
{Aug. 2018 - PRESENT} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\setlength{\itemindent}{.125in}
\item {Became a mentor for a freshman computer engineering major.}
\item {Helped mentee with resume to prepare for career showcase.}
\item {Encouraged mentee to get involved and go to events.}
\end{cvitems}
}

%------------------------------------------------


\end{cventries}